### 2023-06-26 Draft.tex
Added minor adjustments to centering

\usepackage[table]{xcolor}% http://ctan.org/pkg/xcolor
\usepackage{listings}

@@

\begin{abstract}
% +++++++++++++++++++++++++
% Insert your Abstract here (one paragraph summary)
% +++++++++++++++++++++++++
\end{abstract}

@@

\begin{minipage}{\textwidth}\begin{figure}[H]
    \centering
    \subfigure[correlation]{\includegraphics[width=0.19\textwidth]{img/correlation.jpg}}
    \subfigure[convolution]{\includegraphics[width=0.19\textwidth]{img/convolved}}
    \caption{Difference between Correlation and Convolution Filtering by translating 32 pixels}
\end{figure}\end{minipage}

@@

\begin{minipage}{\textwidth}\begin{figure}[H]
    \centering
    \subfigure[zero]{\includegraphics[width=0.19\textwidth]{img/border_constant}}
    \subfigure[wrap]{\includegraphics[width=0.19\textwidth]{img/border_wrap}}
    \subfigure[clamp]{\includegraphics[width=0.19\textwidth]{img/border_clamp}}
    \subfigure[mirror]{\includegraphics[width=0.19\textwidth]{img/border_reflect}}
    \subfigure[extend]{\includegraphics[width=0.19\textwidth]{img/border_extend.jpg}}
    \caption{Different types of border padding}
    \label{fig:padding_borders}
\end{figure}\end{minipage}
\begin{itemize}
    \item \textbf{Zero:} Set all pixels outside the region to zero.
    \item \textbf{Constant:} This is similar to Zero, but instead a specific color is chosen to replace the out of bound pixels.
    \item \textbf{Clamp:} The edge pixels are repeated indefinitely.
    \item \textbf{(Cyclic) Wrap (Repeat or Tile):} The entire image is repeated similar to tiling it infinitely.
    \item \textbf{Mirror:} The image is mirrored accordingly on each of the edges.
    \item \textbf{Extend:} This is a combination of clamping and mirroring, where the clamped image is subtracted with the mirrored image.
\end{itemize}\label{chap:padding}

This of course not only affects the unseen pixels, but the effects can bleed into the pixels inside the frame.
\begin{minipage}{\textwidth}\begin{figure}[H]
    \centering
    \subfigure[zero]{\includegraphics[width=0.19\textwidth]{img/boxBlur_constant}}
    \subfigure[wrap]{\includegraphics[width=0.19\textwidth]{img/boxBlur_wrap}}
    \subfigure[clamp]{\includegraphics[width=0.19\textwidth]{img/boxBlur_clamp}}
    \subfigure[mirror]{\includegraphics[width=0.19\textwidth]{img/boxBlur_reflect}}
    \subfigure[extend]{\includegraphics[width=0.19\textwidth]{img/boxBlur_extend.jpg}}
    \caption{Effects of different paddings with box blur}
    \label{fig:boxBlur_borders}
\end{figure}\end{minipage}

@@

\begin{minipage}{\textwidth}\begin{figure}[H]
    \centering
    \subfigure[original]{\includegraphics[width=0.30\textwidth]{codes/color.jpg}}
    \subfigure[shifted]{\includegraphics[width=0.30\textwidth]{img/colorShift.jpg}}
    \caption{Hue shifting using linear filters of the GALEX telescope image\cite{NASA_on_The_Commons_23}}
    \label{fig:hueshift}
\end{figure}\end{minipage}

@@

This intuitively can be used to reduce the amount of noise on a picture. However, since it naively blurs the entire image,
details are also lost in the process.\\
\begin{minipage}{\textwidth}\begin{figure}[H]
    \centering
    \subfigure[original]{\includegraphics[width=0.32\textwidth]{codes/original_noise.jpg}}
    \subfigure[noise]{\includegraphics[width=0.32\textwidth]{codes/noise.jpg}}
    \subfigure[gaussian]{\includegraphics[width=0.32\textwidth]{img/noiseSuppressed.jpg}}
    \caption{(a) Original image of the Star City Museum\cite{NASA_on_The_Commons_14}(b) Noise added artificially (c) Blurred with Gaussian (k=27 $\sigma=7$)}
    \label{fig:noise}
\end{figure}\end{minipage}

Essentially, the three above filters are different mathematical functions applied both horizontally and vertically.\\
\begin{minipage}{\textwidth}\begin{figure}[H]
    \centering
    \subfigure[Average]{\includegraphics[width=0.29\textwidth]{img/box_graph.png}}
    \subfigure[Bartlett (Tent)]{\includegraphics[width=0.29\textwidth]{img/tent_graph.png}}
    \subfigure[Gaussian]{\includegraphics[width=0.29\textwidth]{img/gaussian_graph.png}}
    \caption{One dimensional graphs of the filters}
    \label{fig:graph}
\end{figure}\end{minipage}
As its name suggests, the Gaussian Filter is based on the Gaussian function (also commonly known as the normal function).
Two dimensionally, it can be expressed as \cite{MISRA2020289}
\[
    G_{2D}(x, y, \sigma) = \frac{1}{2\pi\sigma^2}e^{-\frac{x^2 + y^2}{2\sigma^2}}
\]
It can be seen from the graph that the lower the sigma value, the narrower the neighborhood becomes.

\begin{minipage}{\textwidth}\begin{figure}[H]
    \centering
    \subfigure[Box $(k=133)$]{\includegraphics[width=0.29\textwidth]{img/blurBox.png}}
    \subfigure[Gaussian $(k=233)$]{\includegraphics[width=0.29\textwidth]{img/blurGaussian.png}}
    \caption{Comparison between gaussian and box blur}\label{fig:gauss_box}
\end{figure}\end{minipage}
From Figure \ref{fig:gauss_box}, using the gaussian blur, as opposed to
the box filter produces a more appealing image, as it preserves the shape of the image better as opposed to creating this `halo' effect
and producing a squashed rectangular shape in the center. One disadvantage to Gaussian however is, to produce an equally `blurred' image, a larger kernel is required for Gaussian, which can be argued to then be slower
than using the box filter\cite{Gonzalez_Woods_2018}.

@@

The two sobel operator emphasizes the horizontal or vertical edges respectively, although as seen in the images, it can also highlight diagonal edges.\\
\begin{minipage}{\textwidth}\begin{figure}[H]
    \centering
    \subfigure[original]{\includegraphics*[width=0.29\textwidth]{codes/nasa.jpg}}
    \subfigure[horizontal]{\includegraphics[width=0.29\textwidth]{img/sobelHorizontal.png}}
    \subfigure[vertical]{\includegraphics[width=0.29\textwidth]{img/sobelVertical.png}}
    \caption{Vertical and Horizontal Sobel filtering\cite{NASA_on_The_Commons_2023}}\label{fig:sobel}
\end{figure}\end{minipage}

@@

\begin{minipage}{\textwidth}\begin{figure}[H]
    \centering
    \subfigure[Pattern]{\includegraphics*[width=0.29\textwidth]{codes/pattern.png}}
    \subfigure[Sobel]{\includegraphics[width=0.29\textwidth]{img/directionSobel.png}}
    \subfigure[Prewitt]{\includegraphics[width=0.29\textwidth]{img/directionScharr.png}}
    \caption{Vertical edge detection using Sobel and Prewitt on a test pattern}\label{fig:pattern}
\end{figure}\end{minipage}

@@

\begin{minipage}{\textwidth}\begin{figure}[H]
    \centering
    \subfigure[]{
        {$\begin{bmatrix}
            -1 & 0 & 1 \\
            -2 & 0 & 2 \\
            -1 & 0 & 1
        \end{bmatrix}$}
    }
    \subfigure[]{
        {$\begin{bmatrix}
            1 & 0 & -1 \\
            1 & 0 & -1 \\
            1 & 0 & -1
        \end{bmatrix}$}
    }
    \subfigure[]{
        {$\begin{bmatrix}
            1 & 1 & 1 \\
            0 & 0 & 0 \\
            -1 & -1 & -1
        \end{bmatrix}$}
    }
    \caption{Sobel and Prewitt operator comparison (a) Horizontal Sobel operator; 
    (b) Horizontal Prewitt operator; (c) Vertical Prewitt operator}\label{fig:prewittSobel}
\end{figure}\end{minipage}

Another filter is called the \emph{Laplacian operator}, which is the second (undirected)derivative.\cite{Szeliski_2022}
\[
    \nabla^2 f = \frac{\partial^2 f}{\partial x^2} + \frac{\partial^2 f}{\partial y^2}
\]
and again, it can be smoothed with the Gaussian filter. It is equivalent to the \emph{Laplacian of Gaussian}(LoG) filter.
\[
    \nabla^2 G (x, y, \sigma) = (\frac{x^2 + y^2}{\sigma^4} - \frac{2}{\sigma^2}) G (x, y, \sigma)
\]
\begin{minipage}{\textwidth}\begin{figure}[H]
    \centering
    \subfigure[]{\includegraphics[width=0.29\textwidth]{img/laplacianOriginal.png}}
    \subfigure[]{\includegraphics[width=0.29\textwidth]{img/laplacian.png}}
    \subfigure[]{\includegraphics[width=0.29\textwidth]{img/laplacianAdded.png}}
    \caption{Laplacian Filtering (a) Original image of NASA pilot\cite{NASA_on_The_Commons_1970}; (b) Output of the laplacian filter with Gaussian blur (c) Combined image of the orientation map and original}
    \label{fig:padding_borders}
\end{figure}\end{minipage}

@@

\begin{minipage}{\textwidth}\begin{figure}[H]
    \centering\includegraphics[width=0.60\textwidth]{img/higher.PNG}
    \caption{Fourth-order steerable filter (a) original test pattern (b) average oriented output (c) dominant orientation (d) oriented energy as a function of angle (polar plot)\cite{Szeliski_2022}}
\end{figure}\end{minipage}

@@

\begin{minipage}{\textwidth}\begin{figure}[H]
    \centering
    \subfigure[Original image(S = 24)]{
        $\begin{tabular}{|c|c|c|c|c|}
            \hline 3 & 2 & 7 & 2 & 3 \\
            \hline 1 & \cellcolor{green!25}5 & \cellcolor{green!25}1 & \cellcolor{green!25}3 & 4 \\
            \hline 5 & \cellcolor{green!25}1 & \cellcolor{green!25}\textbf{3} & \cellcolor{green!25}5 & 1 \\
            \hline 4 & \cellcolor{green!25}3 & \cellcolor{green!25}2 & \cellcolor{green!25}1 & 6 \\
            \hline 2 & 4 & 1 & 4 & 8 \\
            \hline
        \end{tabular}$
    }
    \subfigure[Summed area table(S = 28)]{
        $\begin{tabular}{|c|c|c|c|c|}
            \hline 3 & 5 & 12 & 14 & 17 \\
            \hline 4 & \cellcolor{cyan!25}\textit{11} & \cellcolor{cyan!25}\textbf{19} & 24 & 31 \\
            \hline 9 & \cellcolor{cyan!25}\textbf{17} & \cellcolor{red!25}28 & 38 & 46    \\
            \hline 13 & 24 & 37 & 48 & 62 \\
            \hline 15 & 30 & 44 & 59 & 81 \\
            \hline
        \end{tabular}$
    }
    \subfigure[Computation of area sum (S = 24)]{
        $\begin{tabular}{|c|c|c|c|c|}
            \hline \cellcolor{blue!25}\textbf{3} & 5 & 12 & \cellcolor{blue!25}\textit{14} & 17 \\
            \hline 4 & \cellcolor{green!25}11 & \cellcolor{green!25}19 & \cellcolor{green!25}24 & 31 \\
            \hline 9 & \cellcolor{green!25}17 & \cellcolor{green!25}28 & \cellcolor{green!25}38 & 46 \\
            \hline \cellcolor{blue!25}\textit{13} & \cellcolor{green!25}24 & \cellcolor{green!25}37 & \cellcolor{blue!25}\textbf{48} & 62 \\
            \hline 15 & 30 & 44 & 59 & 81 \\
            \hline
        \end{tabular}$
    }
    \caption{Summed area tables\cite{Szeliski_2022}}
    \label{fig:graph}
\end{figure}\end{minipage}
The above table shows the relation of how the area is calculated. For summed area table, the red pixel is calculated by adding itself to the
two highlighted pixels in bold while subtracting the italicised symbol After the entire summed area table is calculated, it is now
cost effective to calculate the area sum as the sum of the top left and bottom right numbers only needs to be subtracted with the other diagonal (remember that
the starting indices requires it to go one pixel beyond the corresponding rectangle).

>>>>

\usepackage[table]{xcolor}% http://ctan.org/pkg/xcolor
\usepackage{listings}
\usepackage{caption}

@@

\begin{abstract}
    Since images are not created the same, and its raw state is not always desired, they can be passed through so called filters to produce an ouput image that is more
    desirable to the viewer. With variations of linear and non-linear filters, many different outcomes can be created for different applications, such as smoothing, image enhancement and edge detection.
    The linear property of linear filters allows it to be simpler and cost effective but still providing useful end images, whereas linear filtering can manufacture a more accurate and desired end result at the cost of  more computer resources.
\end{abstract}

@@

\begin{minipage}{\textwidth}\begin{figure}[H]
    \captionsetup{justification=centering}
    \centering
    \subfigure[correlation]{\includegraphics[width=0.19\textwidth]{img/correlation.jpg}}
    \subfigure[convolution]{\includegraphics[width=0.19\textwidth]{img/convolved}}
    \caption{Difference between Correlation and Convolution Filtering by translating 32 pixels}
\end{figure}\end{minipage}

@@

\begin{minipage}{\textwidth}\begin{figure}[H]
    \captionsetup{justification=centering}
    \centering
    \subfigure[zero]{\includegraphics[width=0.19\textwidth]{img/border_constant}}
    \subfigure[wrap]{\includegraphics[width=0.19\textwidth]{img/border_wrap}}
    \subfigure[clamp]{\includegraphics[width=0.19\textwidth]{img/border_clamp}}
    \subfigure[mirror]{\includegraphics[width=0.19\textwidth]{img/border_reflect}}
    \subfigure[extend]{\includegraphics[width=0.19\textwidth]{img/border_extend.jpg}}
    \caption{Different types of border padding}
    \label{fig:padding_borders}
\end{figure}\end{minipage}
\begin{itemize}
    \item \textbf{Zero:} Set all pixels outside the region to zero.
    \item \textbf{Constant:} This is similar to Zero, but instead a specific color is chosen to replace the out of bound pixels.
    \item \textbf{Clamp:} The edge pixels are repeated indefinitely.
    \item \textbf{(Cyclic) Wrap (Repeat or Tile):} The entire image is repeated similar to tiling it infinitely.
    \item \textbf{Mirror:} The image is mirrored accordingly on each of the edges.
    \item \textbf{Extend:} This is a combination of clamping and mirroring, where the clamped image is subtracted with the mirrored image.
\end{itemize}\label{chap:padding}

This of course not only affects the unseen pixels, but the effects can bleed into the pixels inside the frame.
\begin{minipage}{\textwidth}\begin{figure}[H]
    \captionsetup{justification=centering}
    \centering
    \subfigure[zero]{\includegraphics[width=0.19\textwidth]{img/boxBlur_constant}}
    \subfigure[wrap]{\includegraphics[width=0.19\textwidth]{img/boxBlur_wrap}}
    \subfigure[clamp]{\includegraphics[width=0.19\textwidth]{img/boxBlur_clamp}}
    \subfigure[mirror]{\includegraphics[width=0.19\textwidth]{img/boxBlur_reflect}}
    \subfigure[extend]{\includegraphics[width=0.19\textwidth]{img/boxBlur_extend.jpg}}
    \caption{Effects of different paddings with box blur}
    \label{fig:boxBlur_borders}
\end{figure}\end{minipage}

@@

\begin{minipage}{\textwidth}\begin{figure}[H]
    \captionsetup{justification=centering}
    \centering
    \subfigure[original]{\includegraphics[width=0.30\textwidth]{codes/color.jpg}}
    \subfigure[shifted]{\includegraphics[width=0.30\textwidth]{img/colorShift.jpg}}
    \caption{Hue shifting using linear filters of the GALEX telescope image\cite{NASA_on_The_Commons_23}}
    \label{fig:hueshift}
\end{figure}\end{minipage}

@@

This intuitively can be used to reduce the amount of noise on a picture. However, since it naively blurs the entire image,
details are also lost in the process.\\
\begin{minipage}{\textwidth}\begin{figure}[H]
    \captionsetup{justification=centering}
    \centering
    \subfigure[original]{\includegraphics[width=0.32\textwidth]{codes/original_noise.jpg}}
    \subfigure[noise]{\includegraphics[width=0.32\textwidth]{codes/noise.jpg}}
    \subfigure[gaussian]{\includegraphics[width=0.32\textwidth]{img/noiseSuppressed.jpg}}
    \caption{(a) Original image of the Star City Museum\cite{NASA_on_The_Commons_14}(b) Noise added artificially (c) Blurred with Gaussian (k=27 $\sigma=7$)}
    \label{fig:noise}
\end{figure}\end{minipage}

Essentially, the three above filters are different mathematical functions applied both horizontally and vertically.\\
\begin{minipage}{\textwidth}\begin{figure}[H]
    \captionsetup{justification=centering}
    \centering
    \subfigure[Average]{\includegraphics[width=0.29\textwidth]{img/box_graph.png}}
    \subfigure[Bartlett (Tent)]{\includegraphics[width=0.29\textwidth]{img/tent_graph.png}}
    \subfigure[Gaussian]{\includegraphics[width=0.29\textwidth]{img/gaussian_graph.png}}
    \caption{One dimensional graphs of the filters}
    \label{fig:graph}
\end{figure}\end{minipage}
As its name suggests, the Gaussian Filter is based on the Gaussian function (also commonly known as the normal function).
Two dimensionally, it can be expressed as \cite{MISRA2020289}
\[
    G_{2D}(x, y, \sigma) = \frac{1}{2\pi\sigma^2}e^{-\frac{x^2 + y^2}{2\sigma^2}}
\]
It can be seen from the graph that the lower the sigma value, the narrower the neighborhood becomes.

\begin{minipage}{\textwidth}\begin{figure}[H]
    \captionsetup{justification=centering}
    \centering
    \subfigure[Box $(k=133)$]{\includegraphics[width=0.29\textwidth]{img/blurBox.png}}
    \subfigure[Gaussian $(k=233)$]{\includegraphics[width=0.29\textwidth]{img/blurGaussian.png}}
    \caption{Comparison between gaussian and box blur}\label{fig:gauss_box}
\end{figure}\end{minipage}
From Figure \ref{fig:gauss_box}, using the gaussian blur, as opposed to
the box filter produces a more appealing image, as it preserves the shape of the image better as opposed to creating this `halo' effect
and producing a squashed rectangular shape in the center. One disadvantage to Gaussian however is, to produce an equally `blurred' image, a larger kernel is required for Gaussian, which can be argued to then be slower
than using the box filter\cite{Gonzalez_Woods_2018}.

@@

The two sobel operator emphasizes the horizontal or vertical edges respectively, although as seen in the images, it can also highlight diagonal edges.\\
\begin{minipage}{\textwidth}\begin{figure}[H]
    \captionsetup{justification=centering}
    \centering
    \subfigure[original]{\includegraphics*[width=0.29\textwidth]{codes/nasa.jpg}}
    \subfigure[horizontal]{\includegraphics[width=0.29\textwidth]{img/sobelHorizontal.png}}
    \subfigure[vertical]{\includegraphics[width=0.29\textwidth]{img/sobelVertical.png}}
    \caption{Vertical and Horizontal Sobel filtering\cite{NASA_on_The_Commons_2023}}\label{fig:sobel}
\end{figure}\end{minipage}

@@

\begin{minipage}{\textwidth}\begin{figure}[H]
    \captionsetup{justification=centering}
    \centering
    \subfigure[Pattern]{\includegraphics*[width=0.29\textwidth]{codes/pattern.png}}
    \subfigure[Sobel]{\includegraphics[width=0.29\textwidth]{img/directionSobel.png}}
    \subfigure[Prewitt]{\includegraphics[width=0.29\textwidth]{img/directionScharr.png}}
    \caption{Vertical edge detection using Sobel and Prewitt on a test pattern}\label{fig:pattern}
\end{figure}\end{minipage}

@@

\begin{minipage}{\textwidth}\begin{figure}[H]
    \captionsetup{justification=centering}
    \centering
    \subfigure[]{
        {$\begin{bmatrix}
            -1 & 0 & 1 \\
            -2 & 0 & 2 \\
            -1 & 0 & 1
        \end{bmatrix}$}
    }
    \subfigure[]{
        {$\begin{bmatrix}
            1 & 0 & -1 \\
            1 & 0 & -1 \\
            1 & 0 & -1
        \end{bmatrix}$}
    }
    \subfigure[]{
        {$\begin{bmatrix}
            1 & 1 & 1 \\
            0 & 0 & 0 \\
            -1 & -1 & -1
        \end{bmatrix}$}
    }
    \caption{Sobel and Prewitt operator comparison (a) Horizontal Sobel operator; 
    (b) Horizontal Prewitt operator; (c) Vertical Prewitt operator}\label{fig:prewittSobel}
\end{figure}\end{minipage}

Another filter is called the \emph{Laplacian operator}, which is the second (undirected)derivative.\cite{Szeliski_2022}
\[
    \nabla^2 f = \frac{\partial^2 f}{\partial x^2} + \frac{\partial^2 f}{\partial y^2}
\]
and again, it can be smoothed with the Gaussian filter. It is equivalent to the \emph{Laplacian of Gaussian}(LoG) filter.
\[
    \nabla^2 G (x, y, \sigma) = (\frac{x^2 + y^2}{\sigma^4} - \frac{2}{\sigma^2}) G (x, y, \sigma)
\]
\begin{minipage}{\textwidth}\begin{figure}[H]
    \captionsetup{justification=centering}
    \centering
    \subfigure[]{\includegraphics[width=0.29\textwidth]{img/laplacianOriginal.png}}
    \subfigure[]{\includegraphics[width=0.29\textwidth]{img/laplacian.png}}
    \subfigure[]{\includegraphics[width=0.29\textwidth]{img/laplacianAdded.png}}
    \caption{Laplacian Filtering (a) Original image of NASA pilot\cite{NASA_on_The_Commons_1970}; (b) Output of the laplacian filter with Gaussian blur (c) Combined image of the orientation map and original}
    \label{fig:padding_borders}
\end{figure}\end{minipage}

@@

\begin{minipage}{\textwidth}\begin{figure}[H]
    \captionsetup{justification=centering}
    \centering\includegraphics[width=0.60\textwidth]{img/higher.PNG}
    \caption{Fourth-order steerable filter (a) original test pattern (b) average oriented output (c) dominant orientation (d) oriented energy as a function of angle (polar plot)\cite{Szeliski_2022}}
\end{figure}\end{minipage}

@@

\begin{minipage}{\textwidth}\begin{figure}[H]
    \captionsetup{justification=centering}
    \centering
    \subfigure[Original image(S = 24)]{
        $\begin{tabular}{|c|c|c|c|c|}
            \hline 3 & 2 & 7 & 2 & 3 \\
            \hline 1 & \cellcolor{green!25}5 & \cellcolor{green!25}1 & \cellcolor{green!25}3 & 4 \\
            \hline 5 & \cellcolor{green!25}1 & \cellcolor{green!25}\textbf{3} & \cellcolor{green!25}5 & 1 \\
            \hline 4 & \cellcolor{green!25}3 & \cellcolor{green!25}2 & \cellcolor{green!25}1 & 6 \\
            \hline 2 & 4 & 1 & 4 & 8 \\
            \hline
        \end{tabular}$
    }
    \subfigure[Summed area table(S = 28)]{
        $\begin{tabular}{|c|c|c|c|c|}
            \hline 3 & 5 & 12 & 14 & 17 \\
            \hline 4 & \cellcolor{cyan!25}\textit{11} & \cellcolor{cyan!25}\textbf{19} & 24 & 31 \\
            \hline 9 & \cellcolor{cyan!25}\textbf{17} & \cellcolor{red!25}28 & 38 & 46    \\
            \hline 13 & 24 & 37 & 48 & 62 \\
            \hline 15 & 30 & 44 & 59 & 81 \\
            \hline
        \end{tabular}$
    }
    \subfigure[Computation of area sum (S = 24)]{
        $\begin{tabular}{|c|c|c|c|c|}
            \hline \cellcolor{blue!25}\textbf{3} & 5 & 12 & \cellcolor{blue!25}\textit{14} & 17 \\
            \hline 4 & \cellcolor{green!25}11 & \cellcolor{green!25}19 & \cellcolor{green!25}24 & 31 \\
            \hline 9 & \cellcolor{green!25}17 & \cellcolor{green!25}28 & \cellcolor{green!25}38 & 46 \\
            \hline \cellcolor{blue!25}\textit{13} & \cellcolor{green!25}24 & \cellcolor{green!25}37 & \cellcolor{blue!25}\textbf{48} & 62 \\
            \hline 15 & 30 & 44 & 59 & 81 \\
            \hline
        \end{tabular}$
    }
    \caption{Summed area tables\cite{Szeliski_2022}}
    \label{fig:graph}
\end{figure}\end{minipage}
The above table shows the relation of how the area is calculated. For summed area table, the red pixel is calculated by adding itself to the
two highlighted pixels in bold while subtracting the italicised symbol After the entire summed area table is calculated, it is now
cost effective to calculate the area sum as the sum of the top left and bottom right numbers only needs to be subtracted with the other diagonal (remember that
the starting indices requires it to go one pixel beyond the corresponding rectangle).
